The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-23 paper/ms.tex
one more paragraph in the maxima section

We use the full width at half maximum (FWHM), $W_{1/2}$to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases
with rotational velocity. {\bf Here we need to check the numbers to
  say something more specific.}

We parameterize the dependency of the linewidth as $W_{1/2}^2 =
W_{1/2,0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{1/2,0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for $\lambda = x\pm y$ ($\lambda=x\pm y$) for the central
(homogeneous) sources.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{f4.eps}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{f5_1.eps}
  \includegraphics[width=0.45\textwidth]{f5_2.eps}\\
  \includegraphics[width=0.45\textwidth]{f5_3.eps}
  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
\end{center}
    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
      show the homogeneous (central) source distribution. Left
      corresponds to the static case and the right
      $V_{max}=300km/s$. The color scale is logarithmic on the
      number of photons with given values of $N_{\rm scatt}$ and
      $x$. \label{fig:Nscatt2D}}   
\end{figure*}

The number of \ly photon scatterings affects its final frequency after
escaping the galaxy. In static gas geometries, a large value of the
optical depth correlates with a high number of scatterings, increasing
the probability of finding a \ly photon far from the center of the
line. In these cases the peak maxima shifts away from the line center as
the amount of neutral hydrogen increases.

@@

\item The line width increases with rotational velocity. The line with
  approximately follows the functional form $W_{\rm 1/2}^2 = W_{\rm
    1/2,0}^2 + (V_{\rm max}/\lambda)^2$ where $V_{\rm 1/2,0}$ indicates the line
  width for the static case. $\lambda$ is a constat determined from
  the radiative transfer results it is $\lambda_{\rm c}=XX$ and
  $\lambda_{\rm h}=YY$ for the central and homogeneous source
  distribution, respectively.

>>>>

We use the full width at half maximum (FWHM), $W$, to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how $W$ increases
with rotational velocity. {\bf Here we need to check the numbers to
  say something more specific.}

We parameterize the dependency of the linewidth as $W^2 =
W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for $\lambda = x\pm y$ ($\lambda=x\pm y$) for the central
(homogeneous) sources.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{f4.eps}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{f5_1.eps}
  \includegraphics[width=0.45\textwidth]{f5_2.eps}\\
  \includegraphics[width=0.45\textwidth]{f5_3.eps}
  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
\end{center}
    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
      show the homogeneous (central) source distribution. Left
      corresponds to the static case and right
      $V_{\rm max}=300km/s$. The color scale is logarithmic on the
      number of photons with given values of $N_{\rm scatt}$ and
      $x$. \label{fig:Nscatt2D}}   
\end{figure*}

The number of scatterings affects the escape frequency of a \ly photon.
In static cases, a large value of the optical depth correlates with a
high number of scatterings, increasing the probability of finding a
\ly photon far from the line's center. The result is that he peak maxima
shifts from the center as the amount of neutral hydrogen
increases. This can be precisely quantifyied in for the static slab
with central sources, in that case the maxima position are related to
the optical depth and the temperature as $x_{m}=\pm 1.066(a\tau_{\rm
  H})^{1/3}$ \citep{Harrington73}.

%%%% JEFR.

@@

\item The line width increases with rotational velocity. The line with
  approximately follows the functional form $W^2 = W_{
    0}^2 + (V_{\rm max}/\lambda)^2$ where $W_{0}$ indicates the line
  width for the static case. $\lambda$ is a constat determined from
  the radiative transfer results it is $\lambda_{\rm c}=XX$ and
  $\lambda_{\rm h}=YY$ for the central and homogeneous source
  distribution, respectively.
